Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

\begin{theorem}
Evolving activity satisfies integrity.
\end{theorem}
\begin{proof}
	%TODO
\end{proof}

>>>>

\begin{theorem}
Evolving activity satisfies integrity.
\end{theorem}
\begin{proof}
First we consider the base case, where we add edges to the vertex $v$ at time $t_i$ and $z=0$ initially.

Denote the sum of weights of these new edges by $w(t_i)$, so $z$ decreases to $-\eta w(t_i)$ from 0. By the definition of $z$, we write $z$ as the function of $t$, which is $z(t)=t-t_i-\eta w(t_i)$. For simplify we choose $\mu=e$ here, it's similar to prove for other values of $\mu$. Now the integrity is as follows:

\begin{equation}
\begin{split}
\int_{t_i}^{t_i+\eta w(t_i)} a(G_t,v) dt &= \int_{t_i}^{t_i+\eta w(t_i)} e^{\frac{1}{t-t_i-\eta w(t_i)}} dt \\
&= \int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt.
\end{split}
\end{equation}

Notice that $e^{1/t}<1(t<0)$, so it's easy for this direction
\begin{equation}
\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt< \eta w(t_i).
\end{equation}

Define $f(x)=\int_{-x}^{0} e^{1/t} dt - \frac{x}{10}$, from $f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge 1$. So $f(x)\ge f(1)\approx 0.05>0$.

Now we have the other direction: 
\begin{equation}
\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt>\frac{\eta w(t_i)}{10},
\end{equation}
as long as $\eta w(t_i)\ge 1$.

Next we return to a general case.

We show the theorem holds for each "phase", where we call the period of time when $z<0$ a "phase" and a "phase" starts and ends both with $z=0$. Consider a "phase" starting from $t_i$ and ending at $t_j$, some edges whose sum of weights is $w(t_k)$ are added to $v$ at time $t_k(i\le k\le j)$, so $z$ decreases from $z(t_k)$ to $z(t_k)-\eta w(t_k)$ sharply.

One can verify that
\begin{equation}
\int_{t_i}^{t_j} a(G_t,v) dt< \eta \sum_{k=i}^j w(t_k),
\end{equation}
easily since we still have $\mu^{1/z(t)}<1$.

As for the other direction, notice that at time $t_{k+1}$, there are two cases. One is that $z(t_{k+1})$ has increased equal or above $z(t_k)$, namely we can find some $t_k^*\in (t_k, t_{k+1})$, where $t_k^*$ is defined to satisfy that $z(t_k)=z(t_k^*)$ for all $k$. So we have
\begin{equation}
\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t)}} dt \ge \int_{t_k}^{t_k^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt.
\end{equation}
The other case is that $z(t_{k+1})$ is still less than $z(t_{k})$, in other words, we will find $t_k^*>t_{k+1}$.

Now from
\begin{equation}
z(t)=
\begin{cases}
z(t_k)+t-t_k&  t\in (t_k, t_{k+1})\\
z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2})
\end{cases}
\end{equation}

we have:
\begin{equation}
\begin{split}
\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} dt &\ge \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} dt \\
&= \int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}  dt + \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} -  \mu^{\frac{1}{z(t_{k+1})}} dt + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
&\ge \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt + \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}dt,
\end{split}
\end{equation}
by an easy induction, one can split a "phase" into integrals in the form 
\begin{equation}
\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt
\end{equation}
 Since $ \mu^{1/z}$ decreases as $z$ becomes larger, we can reduce it to the base case now.

Above all, the theorem holds.
\end{proof}
